### 2015-09-15 vmcai-2016-tex/rw.tex
Added a phrase accidentally deleted from rw.tex

\section{Related Work}
\label{sec:related}
%
%\subsection{Program Analysis using Symbolic Heaps}
The symbolic heap methods in this work build upon a
number of prior program analysis techniques that use guarded value sets to
represent program
state~\cite{Sen:2014,Torlak:2014,Xie:2005,Dillig:2011,Elkarablieh:2009}. 
The method was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005}, where value sets were used to 
initialize aliasing-free tree-like heaps. The work in~\cite{Dillig:2011} relaxed the aliasing restrictions by using a pre-computed set of symbolic input heaps, but was instead limited to heaps without recursive data structures.

>>>>

\section{Related Work}
\label{sec:related}
%
%\subsection{Program Analysis using Symbolic Heaps}
The symbolic heap methods in this work build upon a
number of prior program analysis techniques that use guarded value sets to
represent program
state~\cite{Sen:2014,Torlak:2014,Xie:2005,Dillig:2011,Elkarablieh:2009}. In particular, the field write and equals reference compare rules are similar to methods appearing in these works. The real contribution of \symtxt\ is the initialization part of the field access rules which preserves the \gsetxt\ semantics.
Guarded value set heap initialization was pioneered in Verification-Condition Generator (VCG) style techniques such as ~\cite{Xie:2005}, where value sets were used to 
initialize aliasing-free tree-like heaps. The work in~\cite{Dillig:2011} relaxed the aliasing restrictions by using a pre-computed set of symbolic input heaps, but was instead limited to heaps without recursive data structures.
